DMRGenie: Graphical interface for entanglement renormalization

### 2024-12-30 paper/paper.tex
Update paper.tex

K.G. and A.D.~acknowledge the NSERC CREATE in Quantum Computing Program, grant number 543245.

A.D.~acknowledge the Jamie Cassel's Undergraduate Research Award (JCURA). A.D.~acknowledges support from the Undergraduate Student Research Award (USRA) from NSERC.

>>>>

K.G.~and A.D.~acknowledge the NSERC CREATE in Quantum Computing Program, grant number 543245.

A.D.~acknowledges the Jamie Cassel's Undergraduate Research Award (JCURA). A.D.~acknowledges support from the Undergraduate Student Research Award (USRA) from NSERC.
